---
title: "Cumberland County, NJ Data Model A & B Post-Processing Workflow"
output:
  pdf_document:
    toc: yes
    toc_depth: '6'
  html_document:
    toc: yes
    theme: united
    toc_depth: 6
    toc_float: yes
---

```{r clean, include=FALSE}
# a clean slate each time
rm(list=ls())
```

```{r setup, eval=TRUE, include=FALSE, warning=FALSE, messages=FALSE, echo=TRUE, tidy=TRUE, cache=TRUE}
# default to suppress all code chunks unless explicitly indicated
knitr::opts_chunk$set(include=TRUE, warning=FALSE, error=FALSE, tidy=TRUE, results='hide',
                      message=FALSE, echo=FALSE, cache=TRUE, fig.align="center")
```
# Interpreting Model Results

Results from two different models are presented in this document. Model A predicts maltreatment using all referrals, and Model B predicts maltreatment using only referrals that produced an established or substantiated finding.

For each model, both predicted referral counts and predicted risk categories are reported. Risk categories represent quantiles from the model count predictions:

1 = <30th percentile count (lowest risk)
2 = 30th - 50th percentile count
3 = 50th - 70th percentile count
4 = 70th - 90th percentile count
5 = >90th percentile count (highest risk)

# Environment setup

## Packages and functions

The data processing workflow is informed by the [spatialML_package](https://github.com/urbanSpatial/spatialML_package) produced by [UrbanSpatial](http://urbanspatialanalysis.com/) and customized for the State of New Jersey Division of Youth and Family Services.

This work relies on several R packages, imported below:

```{r load-pkgs, warning=FALSE, error=FALSE, tidy=TRUE, results='hide', message=FALSE}
                      
library("sf")            # Spatial data objects and methods
library("ggmap")         # ggplot2 addon for base maps
library("cowplot")
library("raster")        # cell-based spatial operations
library("tidyverse")     # data manipulation framework
library("knitr")         # for kable table
library("viridis")
library("viridisLite")
library("tidycensus")
library("tigris")
library("lubridate")
library("readr")
library("units")
```

We have defined custom several helper functions in `fishnet.r` and `map_themes.r` to assist with data processing and visualization. Load these functions into the environment with the `source()` function.

```{r load-custom-fxns, include=TRUE, echo=TRUE, warning=FALSE, error=FALSE, tidy=TRUE, results='hide', message=FALSE}
source('~/predict-align-prevent/R/sourcefiles/fishnet.r')
source('~/predict-align-prevent/R/sourcefiles/map_themes.r')
```

## Coordinate reference systems

We use two coordinate reference systems (CRS):

- WGS84 is used for map visualizations
- The New Jersey State Planar coordinate reference system is used for euclidean distance calculations that would otherwise be distorted if attempted on an ellipsoid projection such as WGS84.

```{r geometry-constants, include=TRUE, echo=TRUE}
WGS84 = 4326
NAD83 = 4269
NJ_PLANAR = 'ESRI:102311'
```

We also load some generic information about Cumberland County, our area of interest. The `load_neighborhood()` method loads a shapefile of New Jersey counties from the [New Jersey Open Data Portal](https://opendata.arcgis.com/datasets/5f45e1ece6e14ef5866974a7b57d3b95_1.geojson) and converts the CRS to the WGS84 CRS for compatibility with Landscan data. This function also accepts arguments to load data from different areas and can convert to a different CRS if desired.

We use the `extract_area()` method to select Cumberland County from the New Jersey county shapefile, and then use `collect_basemap()` to download a basemap of Cumberland County to use in map visualizations.

```{r neighborhoods-basemaps, include=TRUE, echo=TRUE}
# load and prep general purpose data
nj <- load_neighborhood(
  url='https://opendata.arcgis.com/datasets/5f45e1ece6e14ef5866974a7b57d3b95_1.geojson', 
  crs=NJ_PLANAR)
cumberland <- extract_area(nj)
cumberland_bm <- collect_basemap(cumberland, crs=WGS84)
```

# Population in fishnet grid

```{r fishnet-load}
fishnet <- st_read(
  '~/PredictAlign/PredictAlignFishnets/cumberland_fishnets_urban_areas_with_landscan_NJ_PLANAR.shp'
  )
annual_fishnets <- st_read('~/PredictAlign/PredictAlignFishnets/cumberland_county_halfmi_fishnet_annual_pop.shp')
names(annual_fishnets) <- c('net_id', 'net_pop', 'unitless_net_pop', 'intake_year', 'geometry')
```

Collect the population for each fishnet grid cell from 2017-2019

This block is shown for reference but not run; the file it creates is loaded above under variable name `annual_fishnets`.

```{r fishnet-pop, eval=FALSE}
# years in referral, risk, and protective data (incidents only span 2017-2019)
years <- 2017:2019
resolutions <- c(0.5)
annual_fishnets_list = list() # for storing population fishnets
for(i in seq_along(years)){
  # filter referrals by year
  year_pop <- collect_population(
    key_path='~/CooksProTX/us_census_api_key.txt', 
    year=years[i], 
    crs=NJ_PLANAR
    )
  for(j in seq_along(resolutions)){  # population fishnet
    pop_net <- create_population_fishnet(
      pop_data=year_pop, 
      cover_area=cumberland, 
      fishnet_size=resolutions[j], 
      fishnet_units='mi'
      )
    year_res <- paste(years[i], resolutions[j], sep='_')
    annual_fishnets_list[[year_res]] <- pop_net
  }
}

for(i in seq_along(years)){
  annual_fishnets_list[[i]]$intake_year <- years[i]
}
annual_fishnets <- bind_rows(annual_fishnets_list)
```

```{r save-fishnet, eval=FALSE}
st_write(annual_fishnets, '~/PredictAlign/PredictAlignFishnets/cumberland_county_halfmi_fishnet_annual_pop.shp')
```

```{r population-map, include=TRUE, echo=TRUE, out.width='2000px'}
fishnet_map <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      annual_fishnets, 
      crs=WGS84
      ), aes(fill=unitless_net_pop), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(.~intake_year) +
  scale_fill_viridis(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Cumberland County Population')

fishnet_map

```

# Load all model results

## Model A

```{r modelA-load}
modelA_yearly <- read.csv('~/PAP-NJ-PredictPhase/ModelA_0.5PLANAR/count_predictions_yearly.csv')
modelA_yearly <- modelA_yearly %>% dplyr::select(-'latitude', -'longitude')
modelA_yearly_fishnet <- left_join(fishnet, modelA_yearly, by=c('net_id'='NETID'))
modelA_yearly_fishnet$risk_category_count_change <- modelA_yearly_fishnet$risk_by_count - modelA_yearly_fishnet$risk_by_count_preds
modelA_yearly_fishnet$risk_category_count100_change <- modelA_yearly_fishnet$risk_by_count100 - modelA_yearly_fishnet$risk_by_count100_preds
modelA_yearly_fishnet$risk_by_count_preds <- factor(modelA_yearly_fishnet$risk_by_count_preds, levels=c(1, 2, 3, 4, 5))
modelA_yearly_fishnet$risk_by_count100_preds <- factor(modelA_yearly_fishnet$risk_by_count100_preds, levels=c(1, 2, 3, 4, 5))
modelA_yearly_fishnet$error_count <- modelA_yearly_fishnet$COUNT - modelA_yearly_fishnet$COUNT_preds
modelA_yearly_fishnet$error_count100 <- modelA_yearly_fishnet$COUNT100 - modelA_yearly_fishnet$COUNT100_preds

modelA_avg <- read.csv('~/PAP-NJ-PredictPhase/ModelA_0.5PLANAR/predictions_basedon_yearly_average_full.csv')
modelA_avg <- modelA_avg %>% dplyr::select(-'lat', -'long')
modelA_avg_fishnet <- left_join(fishnet, modelA_avg, by=c('net_id'='NETID'))
modelA_avg_fishnet$risk_by_count_preds <- factor(modelA_avg_fishnet$risk_by_count_preds, levels=c(1, 2, 3, 4, 5))
```

## Model B

```{r modelB-load}
modelB_yearly <- read.csv('~/PAP-NJ-PredictPhase/ModelB_0.5PLANAR/count_predictions_yearly.csv')
modelB_yearly <- modelB_yearly %>% dplyr::select(-'latitude', -'longitude')
modelB_yearly_fishnet <- left_join(fishnet, modelB_yearly, by=c('net_id'='NETID'))
modelB_yearly_fishnet$risk_category_count_change <- modelB_yearly_fishnet$risk_by_count - modelB_yearly_fishnet$risk_by_count_preds
modelB_yearly_fishnet$risk_category_count100_change <- modelB_yearly_fishnet$risk_by_count100 - modelB_yearly_fishnet$risk_by_count100_preds
modelB_yearly_fishnet$risk_by_count_preds <- factor(modelB_yearly_fishnet$risk_by_count_preds, levels=c(1, 2, 3, 4, 5))
modelB_yearly_fishnet$risk_by_count100_preds <- factor(modelB_yearly_fishnet$risk_by_count100_preds, levels=c(1, 2, 3, 4, 5))
modelB_yearly_fishnet$error_count <- modelB_yearly_fishnet$COUNT - modelB_yearly_fishnet$COUNT_preds
modelB_yearly_fishnet$error_count100 <- modelB_yearly_fishnet$COUNT100 - modelB_yearly_fishnet$COUNT100_preds

modelB_avg <- read.csv('~/PAP-NJ-PredictPhase/ModelB_0.5PLANAR/predictions_basedon_yearly_average_full.csv')
modelB_avg <- modelB_avg %>% dplyr::select(-'lat', -'long')
modelB_avg_fishnet <- left_join(fishnet, modelB_avg, by=c('net_id'='NETID'))
modelB_avg_fishnet$risk_by_count_preds <- factor(modelB_avg_fishnet$risk_by_count_preds, levels=c(1, 2, 3, 4, 5))
```

## Standardize binning across models

Counts are converted to binned factors to standardize color palettes across graphs. For both "count" and "count per 100 people" measures, the distribution of predictions has a strong right skew. Most predictions are less than 100 for both measures, so we use the same binning and color palette across all graphs. Additionally, the error measures (yearly predictions only) are binned to positive, negative, and zero categories.

```{r set-bins}
maxAcount <- max(modelA_yearly_fishnet$COUNT_preds)
maxBcount <- max(modelB_yearly_fishnet$COUNT_preds)
max_count_pred <- max(maxAcount, maxBcount)

maxAcount100 <- max(modelA_yearly_fishnet$COUNT100_preds)
maxBcount100 <- max(modelB_yearly_fishnet$COUNT100_preds)
max_count100_pred <- max(maxAcount100, maxBcount100)

cut_sequence <- c(-Inf, seq(0, 100, 10), Inf)
cut_labels <- c(NA, '<10', '10-20', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '>100')
error_sequence <- c(-Inf, -1, 1, Inf)
error_labels <- c('More Predicted', 'Equivalent', 'More Observed')

modelA_yearly_fishnet$count_pred_bin <- cut(modelA_yearly_fishnet$COUNT_preds, cut_sequence, cut_labels)
modelA_yearly_fishnet$count100_pred_bin <- cut(modelA_yearly_fishnet$COUNT100_preds, cut_sequence, cut_labels)
modelA_yearly_fishnet$error_count_bin <- cut(modelA_yearly_fishnet$error_count, error_sequence, error_labels)
modelA_yearly_fishnet$error_count100_bin <- cut(modelA_yearly_fishnet$error_count100, error_sequence, error_labels)

modelB_yearly_fishnet$count_pred_bin <- cut(modelB_yearly_fishnet$COUNT_preds, cut_sequence, cut_labels)
modelB_yearly_fishnet$count100_pred_bin <- cut(modelB_yearly_fishnet$COUNT100_preds, cut_sequence, cut_labels)
modelB_yearly_fishnet$error_count_bin <- cut(modelB_yearly_fishnet$error_count, error_sequence, error_labels)
modelB_yearly_fishnet$error_count100_bin <- cut(modelB_yearly_fishnet$error_count100, error_sequence, error_labels)

modelA_avg_fishnet$count_pred_bin <- cut(modelA_avg_fishnet$COUNT_preds, cut_sequence, cut_labels)
modelB_avg_fishnet$count_pred_bin <- cut(modelB_avg_fishnet$COUNT_preds, cut_sequence, cut_labels)
```

# Model A Results

Model A (Typical PAP model) - To include all CWS and CPS referrals, which would capture all calls, including those with a finding (4 tiers), as well as those without a finding. The unit of analysis is referral per child, which would require allegations to be aggregated when there are multiple allegations per child per referral.

## Annual predictions

### Predicted count

```{r modelA-annual-map, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_count <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=count_pred_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.key.height = unit(0.3, 'cm'),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count')

annual_result_map_count100 <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=count100_pred_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.key.height = unit(0.3, 'cm'),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count per 100 people')

cowplot::plot_grid(annual_result_map_count, annual_result_map_count100, nrow=2)
```

### Nominal Error

```{r modelA-annual-map-error, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_error <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=error_count_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Model A Error, Observed - Predicted Count')

annual_result_map_error100 <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=error_count100_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Model A Error, Observed - Predicted Count per 100 people')

cowplot::plot_grid(annual_result_map_error, annual_result_map_error100, nrow=2)
```

### Predicted risk category

```{r modelA-annual-map-risk, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_risk <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=risk_by_count_preds), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted risk category')

annual_result_map_risk100 <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=risk_by_count100_preds), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted risk category per 100 people')

cowplot::plot_grid(annual_result_map_risk, annual_result_map_risk100, nrow=2)
```

### Risk Category Error

```{r modelA-annual-map-risk_error, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_risk_error <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=risk_category_count_change), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis(
    na.value = NA,
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Model A Count Risk Category Change (Obs - Pred)')

annual_result_map_risk_error100 <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=risk_category_count100_change), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis(
    na.value = NA,
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Model A Count per 100 People Risk Category Change (Obs - Pred)')

cowplot::plot_grid(annual_result_map_risk_error, annual_result_map_risk_error100, nrow=2)
```

## Prediction from yearly average

### Predicted count

```{r modelA-avg-map, include=TRUE, echo=TRUE, out.width='2000px'}
avg_result_map_count <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_avg_fishnet, 
      crs=WGS84
      ), aes(fill=count_pred_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.key.height = unit(0.3, 'cm'),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count based on yearly average')

avg_result_map_count
```

### Predicted risk category

```{r modelA-avg-map-risk}
avg_result_map_count <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelA_avg_fishnet, 
      crs=WGS84
      ), aes(fill=risk_by_count_preds), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted risk category based on yearly average')

avg_result_map_count
```

# Model B

Model B - To include CPS data with an established or substantiated finding. The unit of analysis is referral per child, which would require allegations to be aggregated when there are multiple allegations per child per referral.

## Annual predictions

### Predicted count

```{r modelB-annual-map-risk, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_countB <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=count_pred_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.key.height = unit(0.3, 'cm'),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count')

annual_result_map_count100B <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=count100_pred_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.key.height = unit(0.3, 'cm'),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count per 100 people')

cowplot::plot_grid(annual_result_map_countB, annual_result_map_count100B, nrow=2)
```

### Error

```{r modelB-annual-map-error, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_errorB <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=error_count_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Error, Observed - Predicted Count')

annual_result_map_error100B <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=error_count100_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Model B Error, Observed - Predicted Count per 100 people')

cowplot::plot_grid(annual_result_map_errorB, annual_result_map_error100B, nrow=2)
```

### Predicted risk category

```{r modelB-annual-map, include=TRUE, echo=TRUE, out.width='2000px'}
annual_result_map_countB <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=risk_by_count_preds), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted risk category')

annual_result_map_count100B <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_yearly_fishnet, 
      crs=WGS84
      ), aes(fill=risk_by_count100_preds), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  facet_grid(~ year) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted risk category per 100 people')

cowplot::plot_grid(annual_result_map_countB, annual_result_map_count100B, nrow=2)
```

## Prediction from yearly average

### Predicted count

```{r modelB-avg-map, include=TRUE, echo=TRUE, out.width='2000px'}
avg_result_map_countB <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_avg_fishnet, 
      crs=WGS84
      ), aes(fill=count_pred_bin), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.key.height = unit(0.3, 'cm'),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count based on yearly average')

avg_result_map_countB
```

### Predicted risk category

```{r modelB-avg-map-risk, include=TRUE, echo=TRUE, out.width='2000px'}
avg_result_map_countB_risk <- ggmap(cumberland_bm) + 
  geom_sf(
    data=st_transform(
      modelB_avg_fishnet, 
      crs=WGS84
      ), aes(fill=risk_by_count_preds), inherit.aes = FALSE, color = NA, alpha = 0.8) +
  scale_fill_viridis_d(
    na.value = NA,
    option = "D",
    direction = 1,
    name = ""
  ) +
  mapTheme() +
  theme(
    plot.title = element_text(size = 14, family = "sans", face = "plain", hjust = 0),
    plot.subtitle=element_text(size = 11, family = "sans", hjust = 0),
    plot.caption=element_text(size = 10, family = "sans", face = "italic", hjust = 0),
    axis.line = element_blank(),
    legend.title = element_text(size = 14, family = "sans"),
    legend.text = element_text(size = 9, family = "sans")) +
  labs(title='Predicted count based on yearly average')

avg_result_map_countB_risk
```