---
title: "Align Phase, Cumberland County, NJ Data Processing Workflow"
output:
  pdf_document:
    toc: yes
    toc_depth: '6'
  html_document:
    toc: yes
    theme: united
    toc_depth: 6
    toc_float: yes
---

```{r clean, include=FALSE}
# a clean slate each time
rm(list=ls())
```

```{r setup, include=TRUE, eval=TRUE, warning=FALSE, messages=FALSE, echo=FALSE, cache=FALSE}
# default to suppress all code chunks unless explicitly indicated
knitr::opts_chunk$set(include=TRUE, warning=FALSE, error=FALSE, results='hide',
                      message=FALSE, echo=FALSE, cache=TRUE, fig.align="center")
```

```{r}
library(tidyverse)
library(haven)
library(readxl)
library(readr)
library(lubridate)
library(knitr)
```

# Mortality Data

Required:
- Maternal mortality
- Infant mortality
- Injury-related fatalities
- Fatalities associated with toxic stress

## 2017

Approximately 2k records missing latitude/longitude data.

```{r}
mortality17 <- read_sas('~/Downloads/NJ DCF PAP Project_5-3-2022/NJDOH Mortality Data amf_2017_nossn.sas7bdat')
has_coords17 <- mortality17 %>% 
  filter(amfResidenceLatitude != "" & amfResidenceLongitude != "")
dim(has_coords17)
dim(mortality17)

min(mortality17$amfResidenceLatitude)
max(mortality17$amfResidenceLatitude)

mortality17$year <- lubridate::year(mortality17$amfDateDeath)
```

## 2018

Had to change encoding of ~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Mortality Data_2018.csv to UTF-8 to read file

Approximately 4k records missing latitude/longidute data.

```{r}
mortality18 <- read.csv('~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Mortality Data_2018.csv')
has_coords18 <- mortality18 %>% filter(!is.na(X35..LATITUDE.OF.RESIDENCE) &
                                         !is.na(X36..LONGITUDE.OF.RESIDENCE))
dim(has_coords18)
dim(mortality18)
```

Convert the column names so we can bind with other data

```{r}
mortality18_column_decode <- read_excel('~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Mortality Codebook.xlsx')

mortality18_column_decode$fix_names <- sapply(mortality18_column_decode$Label, make.names)

name_map <- as.list(setNames(mortality18_column_decode$`Variable Name`, mortality18_column_decode$fix_names))

lookup <- function(key){
  if(key %in% names(name_map)){
    return(unname(name_map[[key]]))
  }else{
    return(key)
  }
}

current_names <- names(mortality18)
repair_names <- sapply(current_names, gsub, pattern='í', replacement='.')

fix_names <- sapply(repair_names, lookup)
names(mortality18) <- fix_names
```

Parse death date and add year

```{r}
mortality18$amfDateDeath <- lubridate::parse_date_time(
  mortality18$amfDateDeath,
  orders=c('mdy')
  )

mortality18$year <- lubridate::year(mortality18$amfDateDeath)
```

## 2019

Approximately 3.5k records missing latidute/longidude data.

```{r}
mortality19 <- read_sas('~/Downloads/NJ DCF PAP Project_5-3-2022/NJDOH Mortality Data amf_2019exp.sas7bdat')
has_coords19 <- mortality19 %>% 
  filter(amfResidenceLatitude != "" & amfResidenceLongitude != "")
dim(has_coords19)
dim(mortality19)
mortality19$year <- lubridate::year(mortality19$amfDateDeath)
```

## Combine all years

```{r}
mortality17<-mortality17 %>% 
  mutate(across(everything(), as.character))
mortality18<-mortality18 %>% 
  mutate(across(everything(), as.character))
mortality19<-mortality19 %>% 
  mutate(across(everything(), as.character))
mortality <- bind_rows(mortality17, mortality18, mortality19)

mortality_cumberland <- mortality %>% 
  filter(amfStateResidence == 'NJ' | amfResidenceStateCountry == "NEW JERSEY") %>%
  filter(amfCountyResidence %in% c('11', NA))

mortality_cumberland %>% filter(amfCountyResidence %in% c('11', NA)) %>% group_by(amfCountyResidence) %>% summarise(n=n())
```


```{r}
mortality_to_geocode <- mortality_cumberland %>% 
  filter(amfResidenceLatitude == "" & amfResidenceLongitude == "") %>%
  select(c("amfExpStateOccurrence", "amfPopSizeCountyOccurrence","amfMunicipalityOccurrence","amfStateResidence",
           "amfCountryResidence","amfStateCountryResidenceRecode","amfCountyResidence","amfCityResidence",
           "amfPopSizeCityResidence","amfMetroCountyResidence","amfExpStateResidence","amfPMSAResidence",
           "amfPopSizeCountyResidence","amfPMSAPopSizeResidence","amfCMSAResidence","amfResidenceAddress",
           "amfResidenceCity","amfResidenceStateCountry","amfResidenceZipCode","amfResidenceExpandedZipCode"  ,
           "amfResidenceCountyCode","amfResidenceMunicipalCode","amfResidenceMunicipalityName",
           "amfResidenceLatitude","amfResidenceLongitude")) %>% distinct()
```

Summary stats

```{r}
sufficient_inf <- mortality_to_geocode %>%
  filter(amfResidenceAddress != '') %>% 
  filter(amfResidenceCity != '') %>%
  filter(amfResidenceZipCode != '') %>%
  filter(amfResidenceZipCode != '')

total_obs <- dim(mortality)[1]
total_obs_cumberland <- dim(mortality_cumberland)[1]
total_distinct_obs_cumberland_to_geocode <- dim(mortality_to_geocode)[1]
total_with_sufficient_info <- dim(sufficient_inf)[1]

summary_data <- tibble(
  source=c('morality'),
  total_observations=total_obs,
  total_in_Cumberland=total_obs_cumberland,
  total_in_Cumberland_distinct=total_distinct_obs_cumberland_to_geocode,
  total_in_Cumberland_with_sufficient_inf=total_with_sufficient_info
)
```

```{r}
mortality_to_geocode %>% group_by(amfStateResidence) %>% summarise(n=n())
mortality_to_geocode %>% group_by(amfResidenceStateCountry) %>% summarise(n=n())
mortality_to_geocode %>% group_by(amfCountyResidence) %>% summarise(n=n())

write.csv(mortality_to_geocode, '~/PredictAlign/align-data/NJDOH_Mortality_Data_2017_2018_2019_to_geocode.csv')
write.csv(mortality_cumberland, '~/PredictAlign/align-data/NJDOH_Mortality_Data_2017_2018_2019_CumberlandCounty.csv')
```

# Birth data

Birth data are fixed-width files. There are 760 columns. We don't need them all. We need categories that map to:

Required:
- Maternal mortality
- Infant mortality: "Discharge Status" (3=expired)

Requested:
- Premature birth: 
  - (Birth Weight) Pounds
  - (Birth Weight) Ounces
  - (Birth Weight) Grams
- Very low birth weight: filter on above
- Maternal morbidity: several factors listed, all Y/N.
- Teen birth: filter on column "Mother's Age"
- Drug exposed new borns
  - Alcohol in month before mother knew of pregnancy 1=any, 2=none
  - Any drug (eg. marijuana, cocaine, opioids) in month before pregnancy known 5=no use (!=5 indicates use of some number of days per week)
  - Exposure after pregnancy was known is left blank by NJ DOH
- No prenatal care at birth: "Did mother receive prenatal care?" Y=yes, N=no
  

```{r}
col_widths <- read_excel('~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Birth File Layout.xlsx')

keep_col_names <- c(
  'vipMothersAge',
  'vipMMMaternalTransfusion',
  'vipMMThirdFourthDegree',
  'vipMMRupturedUterus',
  'vipMMUnplannedHyst',
  'vipMMAdmissionToICU',
  'vipMMUnplannedOperatingRoom',
  'vipMMNone',
  'vipMMUnknown',
  'vipWeightinPounds',
  'vipWeightinOunces',
  'vipWeightinGrams',
  'vipDischargeStatus',
  'vipDrinks1MonthBeforePreg',
  'vipSmokes1MonthBeforePreg',
  'vipDrinksDaysWk1MonthBeforePreg',
  'vipDrugsDaysWk1MonthBeforePreg',
  'vipMotherReceivePrenatalCare',
  'vipMothersResStateAbbr',
  'vipMothersResCountyName',
  'vipMothersResTownName',
  'vipMothersResStreetNumber',
  'vipMothersResStreetName',
  'vipMothersResStreetTypeDesc',
  'vipMothersResAptNbr',
  'vipMothersResZip',
  'vipMothersResZipExt',
  'vipGeoMothersResState1',
  'vipGeoMothersResMunicipality',
  'vipGeoMothersResStreet',
  'vipGeoMothersResCity',
  'vipGeoMothersResState',
  'vipGeoMothersResZip',
  'vipGeoMothersResCountyName',
  'vipGeoMothersResMCDFips',
  'vipGeoMothersResMunicipalityName',
  'vipGeoMothersResLatitude',
  'vipGeoMothersResLongitude',
  'vipGeoMothersResTract',
  'vipGeoMothersResBlock',
  'vipGeoMatchScore',
  'vipGeoMatchStatus'
  )

keep_cols <- col_widths %>% filter(VARIABLE_NAME %in% keep_col_names)
```

## 2017

```{r}
birth17 <- readr::read_fwf(
  '~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Birth Data_2017.txt',
  fwf_positions(start=keep_cols$START, end=keep_cols$END, col_names=keep_cols$VARIABLE_NAME))
```

```{r}
bad_rows_17 <- problems()
```

```{r}
cumberland17 <- birth17 %>% filter(vipMothersResCountyName %in% c('CUMBERLAND', NA) & vipMothersResTownName %in% c('MILLVILLE', 'VINELAND', 'COMMERCIAL TOWNSHIP', 'BRIDGETON') & vipMothersResStateAbbr == 'NJ')

missing_county <- cumberland17 %>% filter(is.na(vipMothersResCountyName))
wrong_county <- cumberland17 %>% filter(!is.na(vipMothersResCountyName) & vipMothersResCountyName != 'CUMBERLAND')

has_coords_brith17 <- cumberland17 %>% 
  filter(!is.na(vipGeoMothersResLatitude) & !is.na(vipGeoMothersResLongitude))
dim(has_coords_brith17)
dim(cumberland17)
```

## 2018

```{r}
birth18 <- readr::read_fwf(
  '~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Birth Data_2018.txt',
  fwf_positions(start=keep_cols$START, end=keep_cols$END, col_names=keep_cols$VARIABLE_NAME))
```

```{r}
cumberland18 <- birth18 %>% filter(vipMothersResCountyName %in% c('CUMBERLAND', NA) & vipMothersResTownName %in% c('MILLVILLE', 'VINELAND', 'COMMERCIAL TOWNSHIP', 'BRIDGETON') & vipMothersResStateAbbr == 'NJ')

missing_county <- cumberland18 %>% filter(is.na(vipMothersResCountyName))
wrong_county <- cumberland18 %>% filter(!is.na(vipMothersResCountyName) & vipMothersResCountyName != 'CUMBERLAND')

has_coords_brith18 <- cumberland18 %>% 
  filter(!is.na(vipGeoMothersResLatitude) & !is.na(vipGeoMothersResLongitude))
dim(has_coords_brith18)
dim(cumberland18)
```

## 2019

```{r}
birth19 <- readr::read_fwf(
  '~/Downloads/NJ DCF PAP Project_5-3-2022/NJ DOH Birth Data_2019.txt',
  fwf_positions(start=keep_cols$START, end=keep_cols$END, col_names=keep_cols$VARIABLE_NAME))
```

```{r}
bad_rows_19 <- problems()
```

```{r}
cumberland19 <- birth19 %>% filter(vipMothersResCountyName %in% c('CUMBERLAND', NA) & vipMothersResTownName %in% c('MILLVILLE', 'VINELAND', 'COMMERCIAL TOWNSHIP', 'BRIDGETON') & vipMothersResStateAbbr == 'NJ')

missing_county <- cumberland19 %>% filter(is.na(vipMothersResCountyName))
wrong_county <- cumberland19 %>% filter(!is.na(vipMothersResCountyName) & vipMothersResCountyName != 'CUMBERLAND')

has_coords_brith19 <- cumberland19 %>% 
  filter(!is.na(vipGeoMothersResLatitude) & !is.na(vipGeoMothersResLongitude))
dim(has_coords_brith19)
dim(cumberland19)
```

## Combine all years

```{r}
cumberland17<-cumberland17 %>% 
  mutate(year=2017) %>% 
  mutate(across(everything(), as.character))
cumberland18<-cumberland18 %>% 
  mutate(year=2018) %>% 
  mutate(across(everything(), as.character))
cumberland19<-cumberland19 %>% 
  mutate(year=2019) %>% 
  mutate(across(everything(), as.character))


cumberland_birth <- bind_rows(cumberland17, cumberland18, cumberland19)

```

```{r}
to_geocode <- cumberland_birth %>% 
  filter(is.na(vipGeoMothersResLatitude) & is.na(vipGeoMothersResLongitude)) %>%
  select(c("vipMothersResStateAbbr","vipMothersResCountyName","vipMothersResTownName","vipMothersResStreetNumber",
           "vipMothersResStreetName","vipMothersResStreetTypeDesc","vipMothersResAptNbr","vipMothersResZip",
           "vipMothersResZipExt")) %>%
  distinct()
```

```{r}
sufficient_inf_birth <- to_geocode %>%
  filter(vipMothersResStreetNumber != '') %>%
  filter(vipMothersResTownName != '') %>% 
  filter(vipMothersResStreetName != '') %>%
  filter(vipMothersResStreetTypeDesc != '') %>%
  filter(vipMothersResZip != '')

total_obs_birth <- dim(birth17)[1] + dim(birth18)[1] + dim(birth19)[1]
total_obs_cumberland_birth <- dim(cumberland_birth)[1]
total_distinct_obs_cumberland_to_geocode_birth <- dim(to_geocode)[1]
total_with_sufficient_info_birth <- dim(sufficient_inf_birth)[1]

summary_data_birth <- tibble(
  source=c('birth'),
  total_observations=total_obs_birth,
  total_in_Cumberland=total_obs_cumberland_birth,
  total_in_Cumberland_distinct=total_distinct_obs_cumberland_to_geocode_birth,
  total_in_Cumberland_with_sufficient_inf=total_with_sufficient_info_birth
)

final_summary <- bind_rows(summary_data_birth, summary_data)
kable(final_summary)

```


```{r}
write.csv(to_geocode, '~/PredictAlign/align-data/NJ_DOH_Birth_Data_2017_2018_2019_to_geocode.csv')
write.csv(cumberland_birth, '~/PredictAlign/align-data/NJ_DOH_Birth_Data_2017_2018_2019_CumberlandCounty.csv')

```