---
title: "Census Variables, Cumberland County, NJ Data Processing Workflow"
output:
  pdf_document:
    toc: yes
    toc_depth: '6'
  html_document:
    toc: yes
    theme: united
    toc_depth: 6
    toc_float: yes
---

```{r clean, include=FALSE}
# a clean slate each time
rm(list=ls())
```

```{r setup, include=TRUE, eval=TRUE, warning=FALSE, messages=FALSE, echo=FALSE, cache=FALSE}
# default to suppress all code chunks unless explicitly indicated
knitr::opts_chunk$set(include=TRUE, warning=FALSE, error=FALSE, results='hide',
                      message=FALSE, echo=FALSE, cache=TRUE, fig.align="center")
```

# Risk and Protective Factor Data Processing Description

We use half-mile and landscan to aggregate the geocoded risk and protective factor data. These aggregations are then used to contextualize child maltreatment risk in terms of these factors. 

# Environment setup

The following packages define the environment required for this workflow:

```{r load-pkgs, include=TRUE, echo=TRUE}
library("sf")            # Spatial data objects and methods
library("ggmap")         # ggplot2 addon for base maps
library("cowplot")
library("raster")        # cell-based spatial operations
library("tidyverse")     # data manipulation framework
library("knitr")         # for kable table
library("viridis")
library("viridisLite")
library("tidycensus")
library("tigris")
library("lubridate")
library("readr")
library("units")
```

As with the Model A pre-processing workflow, we load a series of helper functions, assign global variables, and load basemaps for plotting as part of our environment setup.

```{r load-custom-fxns, eval=TRUE, include=TRUE, echo=TRUE}
source('~/predict-align-prevent/R/sourcefiles/fishnet.r', local = knitr::knit_global())
source('~/predict-align-prevent/R/sourcefiles/map_themes.r', local = knitr::knit_global())
```

```{r geometry-constants, include=TRUE, echo=TRUE}
WGS84 = 4326
NAD83 = 4269
NJ_PLANAR = 'ESRI:102311'
```

```{r neighborhoods-basemaps, include=TRUE, echo=TRUE}
# load and prep general purpose data
nj <- load_neighborhood(
  url='https://opendata.arcgis.com/datasets/5f45e1ece6e14ef5866974a7b57d3b95_1.geojson', 
  crs=NJ_PLANAR
  )
cumberland <- extract_area(nj)
cumberland_bm <- collect_basemap(cumberland, crs=WGS84)
```

# Load fishnets

These fishnets were created during the pre-processing for Model A, but are not specific to that model type. We load a single shapefile containing fishnets for both the half-mile and landscan grids, and split the dataset into those respective grid dataframes.

```{r save-halfmi-fishnet, eval=TRUE, include=TRUE, echo=TRUE}
# .prj file shows correct projection, but crs(fishnet) does not
# transform to be sure it's right
fishnet <- st_read(
  '~/PredictAlign/PredictAlignFishnets/cumberland_fishnets_urban_areas_with_landscan_NJ_PLANAR.shp'
  ) 
# fix names shortened by ESRI shapefile driver
names(fishnet) <- c(  
  'net_id', 'net_pop', 'year', 'fn_width', 'include_area',
  'in_Commercial_Township', 'in_Bridgeton', 'in_Millville',
  'in_Vineland', 'geometry')

fishnet_half_mile <- fishnet %>% filter(fn_width=='0.5') %>% 
  dplyr::select(-net_pop, -year) %>% 
  distinct()
fishnet_landscan <- fishnet %>% filter(fn_width=='landscan') %>% 
  dplyr::select(-net_pop, -year) %>% 
  distinct()
```

# Load census data

Data were downloaded on April 14 2022 using command ` Rscript census_aggregato.r -k /Users/kpierce/CooksProTX/us_census_api_key.txt -s PAP-NJ/PAP-NJ-Variables -o /Users/kpierce/PredictAlign` to pull variables listed in the Google Drive sheet `PAP-NJ/PAP-NJ-Variables`. That sheet maps the column names in the file loaded below to alphanumeric data identifiers used by the US Census Bureau to label data.

```{r census-load}
census <- read.csv('~/PredictAlign/PAP-NJ-Variables_20220607190202.csv')
census$GEOID <- as.character(census$GEOID)

# tract level population data (just to get shapes)
tract17 <- get_acs(
    geography='tract',
    variables='B01003_001',
    state='NJ',
    county='Cumberland',
    year=2017,
    survey='acs5',
    show_call=TRUE,
    geometry=TRUE
  ) %>% st_transform(crs=NJ_PLANAR)

tract18 <- get_acs(
    geography='tract',
    variables='B01003_001',
    state='NJ',
    county='Cumberland',
    year=2018,
    survey='acs5',
    show_call=TRUE,
    geometry=TRUE
  ) %>% st_transform(crs=NJ_PLANAR)

tract19 <- get_acs(
    geography='tract',
    variables='B01003_001',
    state='NJ',
    county='Cumberland',
    year=2019,
    survey='acs5',
    show_call=TRUE,
    geometry=TRUE
  ) %>% st_transform(crs=NJ_PLANAR)

tract17$year <- 2017
tract18$year <- 2018
tract19$year <- 2019
tract_shapes <- bind_rows(tract17, tract18, tract19)

census$GEOID <- as.character(census$GEOID)
```

# Merge census data and census tract shapes

```{r}
census_shapes <- left_join(
  census,
  tract_shapes,
  on=c('GEOID', 'year')
) %>% filter(grepl('Cumberland County', NAME)) %>%
  st_as_sf(crs=NJ_PLANAR)

census_shapes$block_area <- st_area(census_shapes)
```

# Calculate outstanding variables

Some percentages must be calculated. We won't calculate population density here; we'll do that after rasterizing the population values.

```{r}
# Percent non-white
census_shapes$EP_NON_WHITE <- census_shapes$E_NON_WHITE / census_shapes$E_TOTPOP

# Percent non-married
census_shapes$EP_NON_MARRIED <- (census_shapes$E_HH - census_shapes$E_HH_MARRIED) / census_shapes$E_HH

# Select final variables
census_shapes_pct <- census_shapes %>% 
  select(GEOID, year, E_TOTPOP, EP_BLACK, EP_NON_WHITE, EP_HISPANIC_LATINO, EP_AGE17, EP_COLLEGE_ED,
         EP_NOHSDP, EP_POV, EP_SNGPNT, EP_HH_FEMALE_HEADED, EP_NON_MARRIED, EP_PUBLIC_INSURANCE,
         EP_UNINSUR, EP_HU_OWNER_OCCUPIED, EP_RENTER_OCCUPIED, geometry, block_area)
```

# Rasterize variables

```{r, eval=FALSE}
variables <- names(census_shapes_pct)[grepl('EP_', names(census_shapes_pct))]

years <- 2017:2019
variable_fishnets_list = list() # for storing variable fishnets
for(i in seq_along(years)){
  # filter referrals by year
  year_census <- census_shapes_pct %>% filter(year==years[i])
  for(j in seq_along(variables)){  # population fishnet
    print(
      paste("Processing year", years[i], "and variable", variables[j], sep=' ')
      )
    year_census_var <- year_census %>%
      select(GEOID, block_area, variables[j]) %>%
      rename('estimate' = variables[j])
    pop_net <- create_population_fishnet(
      pop_data=year_census_var, 
      cover_area=cumberland, 
      fishnet_size=0.5, 
      fishnet_units='mi'
      )
    net_name <- paste(years[i], variables[j], sep='_')
    variable_fishnets_list[[net_name]] <- pop_net
  }
}
```

That took about 2h, let's save the list of rasterized census data...

```{r}
saveRDS(variable_fishnets_list, '~/PredictAlign/census_variable_fishnets_june2022.rds')
```

```{r}
rasters2017 <- list()
rasters2018 <- list()
rasters2019 <- list()
for(l in seq_along(variable_fishnets_list)){
  indicators <- unlist(strsplit(names(variable_fishnets_list)[l], split='_'))
  varname <- paste(indicators[2:length(indicators)], collapse='_')
  print(varname)
  data_item <- variable_fishnets_list[[l]]
  names(data_item)[names(data_item) == 'net_pop'] <- varname
  data_item <- data_item %>% select(-unitless_net_pop)
  if(indicators[1] == '2017'){
    rasters2017[[varname]]  <- data_item
  }else if(indicators[1] == '2018'){
    rasters2018[[varname]]  <- data_item
  }else if(indicators[1] == '2019'){
    rasters2019[[varname]]  <- data_item
  }
}

all2017 <- rasters2017[[1]]
for(i in 2:length(rasters2017)){
  joindata <- rasters2017[[i]] %>% st_drop_geometry()
  all2017 <- left_join(all2017, joindata, on='net_id')
}
all2017$year <- 2017

all2018 <- rasters2018[[1]]
for(i in 2:length(rasters2018)){
  joindata <- rasters2018[[i]] %>% st_drop_geometry()
  all2018 <- left_join(all2018, joindata, on='net_id')
}
all2018$year <- 2018

all2019 <- rasters2019[[1]]
for(i in 2:length(rasters2019)){
  joindata <- rasters2019[[i]] %>% st_drop_geometry()
  all2019 <- left_join(all2019, joindata, on='net_id')
}
all2019$year <- 2019

all_census_rasters <- bind_rows(all2017, all2018, all2019)
write.csv(
  (all_census_rasters %>% st_drop_geometry()),
  '~/PredictAlign/census_variable_fishnets_half_mi_ESRI_102311.csv')
st_write(all_census_rasters, '~/PredictAlign/census_variable_fishnets_half_mi_ESRI_102311.shp')
```

# Do it all again for the landscan fishnet

```{r, eval=FALSE}
# same as create_population_fishnet(), just picks up at the `net_agg` step, where
# the landscan fishnet serves as the `net_agg` fishnet grid object
create_population_fishnet_landscan <- function(pop_data, net_agg, cover_area, fishnet_size, fishnet_units='mi'){
  
  # list of net cells IDs that intersect with the cover area (if cover area is irregular)
  print('Intersecting fishnet with population data.')
  net_intersect <- st_intersects(cover_area, net_agg) 
  net_cover_area <- net_agg[unique(unlist(net_intersect)),]
  net_cover_area$net_area <- st_area(net_cover_area)
  net_blocks_intersect <- st_intersection(pop_data, net_cover_area)
  print(paste('Dimensions of intersection data', 
              dim(net_blocks_intersect), sep=': '))
  
  # group by fishnet cell and calc block stats.
  print('Calculating block and fishnet intersection areas.')
  net_blocks_intersect <- net_blocks_intersect %>%
    # calculate the area of each tract/fishet intersection
    mutate(intersect_area = st_area(net_blocks_intersect) ) %>%
    # group by the fishnet ID
    group_by(net_id) %>%
    # calculate the fraction of each block group covered by a fishnet cell
    # then assume the population is proportional to the overlap area
    mutate(
      cnt = n(), 
      pcnt_of_block = intersect_area/block_area, 
      intersect_pop = estimate * pcnt_of_block) %>%
    arrange(net_id)
  
  print('Summarizing fishnet population sizes.')
  fishnet_pop <- net_blocks_intersect %>%
    group_by(net_id) %>%
    summarise(net_pop = sum(intersect_pop)) 
  
  # drop units (required for plotting)
  fishnet_pop$unitless_net_pop <- units::drop_units(fishnet_pop$net_pop)
  
  return(fishnet_pop)
}

census2019 <- census_shapes %>% filter(year==2019)
variable_fishnets_list_landscan <- list()
for(j in seq_along(variables)){  # population fishnet
  print(
    paste("Processing 2019 variable", variables[j], sep=' ')
    )
  census2019_var <- census2019 %>%
    select(GEOID, block_area, variables[j]) %>%
    rename('estimate' = variables[j])
  pop_net <- create_population_fishnet_landscan(
    pop_data=census2019_var,
    net_agg=fishnet_landscan,
    cover_area=cumberland, 
    fishnet_size=0.5, 
    fishnet_units='mi'
    )
  net_name <- variables[j]
  variable_fishnets_list_landscan[[net_name]] <- pop_net
}

# grab just the net_id and geometry columns
all_landscan_census <- variable_fishnets_list_landscan[[1]] %>%
  select(net_id, geometry)
for(l in seq_along(variable_fishnets_list_landscan)){
  # grab the data and rename the `net_pop` column to the variable name
  data_item <- variable_fishnets_list_landscan[[l]]
  names(data_item)[names(data_item) == 'net_pop'] <- names(variable_fishnets_list_landscan)[l]
  data_item <- data_item %>% select(-unitless_net_pop) %>% st_drop_geometry()
  all_landscan_census <- left_join(all_landscan_census, data_item, on='net_id')
}
 
all_landscan_census$year <- 2019
write.csv((all_landscan_census %>% st_drop_geometry()),
          '~/PredictAlign/census_variable_fishnets_landscan_ESRI_102311.csv')
st_write(all_landscan_census, '~/PredictAlign/census_variable_fishnets_landscan_ESRI_102311.shp')

```